Distinguishing Between Spin-Aligned and Isotropic Binary Black Hole Populations in Advanced LIGO

### 2017-01-21 paper/AlignedIsotropicGW.tex
Dumped a couple of references in intro.

\newcommand{\chieff}{\chi_\mathrm{eff}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\diff}[2]{\frac{\dd #1}{\dd #2}}
\newcommand{\pali}{p_\mathrm{ali}}
\newcommand{\piso}{p_\mathrm{iso}}

@@

>>>>

\newcommand{\chieff}{\chi_\mathrm{eff}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\diff}[2]{\frac{\dd #1}{\dd #2}}
\newcommand{\fixme}[1]{\textcolor{red}{FIXME: #1}}
\newcommand{\pali}{p_\mathrm{ali}}
\newcommand{\piso}{p_\mathrm{iso}}

@@

We should be sure to discuss \citet{Rodriguez2016} here; they note the
small $\chieff$ of GW150914, but only in the context of looking for a
single system that is \emph{definitely} formed from dynamical
interactions; obviously, the population provides a more stringent
origin test.

We find much higher resolving power than \citet{Vitale2015}, probably
because they focus on measurements of spin \emph{angles}, using a
mixture model comprising an aligned and isotropic component.

\citet{Miller2015} summarises the current best \ac{EM} constraints on
the black hole spin distribution; it is consistent with flat but could
be increasing toward large spins (\fixme{Cole: can you confirm and
  summarise better?}).
